\Large \bf Module-level Dynamic Analysis

### 2019-12-19 paper/draft.tex
Update prelude and intro

\documentclass[letterpaper,twocolumn,10pt]{article}
\usepackage{usenix2019_v3}

\usepackage{soul}
\usepackage{xspace}
\usepackage{color}
\newcommand{\eg}{{\em e.g.}, }
\newcommand{\ie}{{\em i.e.}, }
\newcommand{\etc}{{\em etc.}\xspace}
\newcommand{\vs}{{\em vs.} }

\newcommand{\cf}[1]{(\emph{Cf}.\S\ref{#1})}
\newcommand{\sx}[1]{(\S\ref{#1})}
\newcommand{\sys}{{\scshape Lya}\xspace}
\newcommand{\toy}{{\tt lya.js}\xspace}
%-------------------------------------------------------------------------------
\begin{document}
%-------------------------------------------------------------------------------

@@

%for single author (just remove % characters)
\author{
{\rm Grigoris Ntousakis}\\
Technical University of Crete
\and
{\rm Nikos Vasilakis}\\
Massachusetts Institute of Technology
}

@@

\begin{abstract}
We introduce \emph{module-level dynamic analysis}, a new dynamic analysis abstraction that supports dynamic fracture and recombination at the level of individual modules.
By leveraging the ubiquity of third-party modules in today's applications, this analysis provides 
Our implementation, \sys, simplifies the analysis

>>>>

% TODO: tempted to term this "Module-aware dynamic fracture, analysis, and reassembly" as Dialysis or refracture
\documentclass[letterpaper,twocolumn,10pt]{article}
\usepackage{usenix2019_v3}

\usepackage{soul}
\usepackage{xspace}
\usepackage{color}

\def\omit#1{}
\def\eg{{\em e.g.}, }
\def\ie{{\em i.e.}, }
\def\etc{{\em etc.}\xspace}
\def\vs{{\em vs.}\xspace}
% \newcommand{\heading}[1]{\vspace{4pt}\noindent\textbf{#1}\enspace}
% No vspace, coz Usenix class already has paragraph space
\newcommand{\heading}[1]{\vspace{2pt}\noindent\textbf{#1}\enspace}
\newcommand{\ttt}[1]{\texttt{#1}}
\newcommand{\ttiny}[1]{\texttt{\scriptsize #1}}
\newcommand{\tcn}[1]{}

\newcommand{\cf}[1]{(\emph{Cf}.\S\ref{#1})}
\newcommand{\sx}[1]{(\S\ref{#1})}
\newcommand{\sys}{{\scshape Lya}\xspace}
\newcommand{\toy}{{\tt lya.js}\xspace}

\newcommand{\nv}[1]{[{\color{cyan}#1 --- Nikos}]}
\newcommand{\review}[1]{{\color{red}#1}}
\newcommand{\TODO}[1]{\hl{\textbf{TODO:} #1}\xspace}
\newcommand{\todo}[1]{\hl{#1}\xspace}
\newcommand{\fixme}[1]{{\color{red}#1}}
\newcommand{\tc}{(\todo{cite})\xspace}
%-------------------------------------------------------------------------------
\begin{document}
%-------------------------------------------------------------------------------

@@

%for single author (just remove % characters)
\author{
{\rm Anonymous Author(s)}\\
Submission \#323, 12 pages; Additional Material:
% {\rm Grigoris Ntousakis}\\
% Technical University of Crete
% \and
% {\rm Nikos Vasilakis}\\
% Massachusetts Institute of Technology
}

@@

\begin{abstract}
Modern software relies extensive on third-party libraries:
  recent studies on several ecosystems show that code written by an application's nominal developers is only a small fraction of its total line count.
Such over-reliance creates many challenges that appear later in the development process, exactly because developers have little knowledge and understanding of the module's internals.
For example, security auditing and performance profiling large applications in the presence of deeply-nested third-party code becomes cumbersome.

We introduce \emph{module dialysis}, a technique for dynamic analysis specifically tailored to module boundaries.
Module dialysis can be bolted on existing language runtime environments in a language-agnostic fashion, and enables module-aware application fracture, analysis, and reassembly at runtime.
Dialysis supports dynamic application fragmentation, analysis, and re-assembly at the level of individual modules.
Tailored at providing information at the (recursive) boundaries of third-party modules.
Such modules can be part of third-party packages or of the language's standard library;
  the latter is important for resources that are part of the broader environment where the application is executing, such as the operating system and the network.
By leveraging the ubiquity of third-party modules in today's applications, this analysis provides insights k

We use a series of case-study analyses to motivate \sys's design and demonstrate how \sys provides high-performance by shadowing variables and transforming and wrapping values

, all with minimal developer effort.
The key feature is that module-level analysis can be bolted onto existing runtime environments as a library, without requiring low-level intsrumentation and maintaing the semantics of..
Measurements of two COWL implementations, one in Firefox and one in Chromium, demonstrate a virtually imperceptible increase in page-load latency.

Our implementation, \sys, simplifies the analysis
